Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-05-18 paper/paper.tex
Plots with fewer dots, more significance tests
Notes, daily difference significance test

@@

\begin{figure}[tp!]
	\centering
	\includegraphics[scale=0.40]{figures/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
	\includegraphics[scale=0.40]{figures/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
	\label{fig:RhoBinned}
\end{figure}

>>>>

\input{../tables/DeltaBootstraps.txt}

@@

\begin{figure}[tp!]
	\centering
	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
	\label{fig:RhoBinned}
\end{figure}
